PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-12 qfenv_paper/qf_environment.tex
Iovino error bars removed
Text appropriately corrected for panel change.

\def \iovinopanel {b}
\def \kovacpanel {c}
\def \pengpanel {d}
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset_4panel.eps, height=\textwidth, angle=90}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} (filled square) from both SDSS and zCOSMOS (panel \pengpanel). The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works. The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. High density environment is represented in red and low density environment is represented in blue. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure*}

@@

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel$ $ and \kovacpanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
%$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
%\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
From \cite{Iovino:2010aa} (empty square; panel \iovinopanel$ $ in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel$ $ in Figure \ref{fig:qffit_comp})
we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
based and color based galaxy classifications to the best-fit
$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
low ($\delta = 0.0$) and high density environments ($\delta =
1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a in Figure \ref{fig:qffit_comp}) we plot $f_{\rm{Q}}$
derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a in Figure \ref{fig:qffit_comp}), we plot $f_{\rm{Q}}$
for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. Finally for \cite{Peng:2010aa} (square; panel \pengpanel$ $ in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.

>>>>

\def \iovinopanel {b}
\def \kovacpanel {b}
\def \pengpanel {c}
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr_baldry_geha_iovino_kovac_peng_envthresh_kovacoffset.eps, height=\textwidth, angle=90}
        \caption{$f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\rm{red}}(\mathcal{M}_{*}=10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square; panel \iovinopanel) and \cite{Kovac:2014aa} (triangle; panel \kovacpanel) from zCOSMOS, and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel). The $f_{\rm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works. The $f_{\rm{Q}}$ value from \cite{geha12a} is the $f_{\rm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. High density environment is represented in red and low density environment is represented in blue. The uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\rm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\rm{Q}}$ estimates. We also plot the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure*}

@@

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of
$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), zCOSMOS (panel \iovinopanel), and \cite{Peng:2010aa} (filled square; panel d) from both surveys. 
%$f_{\rm{red}}$ for high and low density environment from SDSS (panel a), \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross), zCOSMOS (panel b),
%\cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle), and \cite{Peng:2010aa} (filled square; panel c) from both surveys. From
From \cite{Iovino:2010aa} (empty square; panel \iovinopanel$ $ in Figure \ref{fig:qffit_comp}), we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$
using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} =
10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} (triangle; panel \kovacpanel$ $ in Figure \ref{fig:qffit_comp})
we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR
based and color based galaxy classifications to the best-fit
$f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for
low ($\delta = 0.0$) and high density environments ($\delta =
1.5$). Similarly, from \cite{Baldry:2006aa} (diamond; panel a in Figure \ref{fig:qffit_comp}) we plot $f_{\rm{Q}}$
derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5}
\mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density
environment ($\delta = 1.0$). For \cite{geha12a} (cross; panel a in Figure \ref{fig:qffit_comp}), we plot $f_{\rm{Q}}$
for their isolated galaxy sample in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. Finally for \cite{Peng:2010aa} (square; panel \pengpanel$ $ in Figure \ref{fig:qffit_comp}), we plot the parameterized $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ using their best-fit parameters for low ($\delta =0.0$) and high ($\delta = 1.4$) density environments.
